### 2020-08-01 ReadMe.rmd
fix badge readme
udpates
update sreadme

### M.Sc. Thesis Code

>>>>

### M.Sc. Thesis 2018-2020

![Docker image build](https://github.com/VLucet/landchange-connectivity-monteregie/workflows/Build%20/%20Push%20Docker%20image/badge.svg)

[GitHub page](https://vlucet.github.io/landchange-connectivity-monteregie/)

[Thesis](https://github.com/VLucet/landchange-connectivity-monteregie/blob/master/thesis/build/thesis.pdf)
